% !TEX program = xelatex

\documentclass{resume}

% \usepackage{lastpage}
% \usepackage{fancyhdr}
\usepackage{linespacing_fix} % disable extra space before next section

\begin{document}
% \pagestyle{fancy}
% \fancyhf{}
% \renewcommand\headrulewidth{0pt}
% \cfoot{\thepage\ of \pageref{LastPage}}

\name{Yichen Yan}

\basicInfo{
  \email{oraluben@outlook.com} \textperiodcentered\ 
  \phone{(+86) 189-1807-5127} \textperiodcentered\
  \github[oraluben]{https://github.com/oraluben}
}

\section{Work Experience}
\datedsubsection{\textbf{Alibaba Cloud}, Shanghai}{03/2022 -- now}
\role{Senior Engineer}{Runtime optimization for CPython/Node.js and architecture-specific optimization}
% \begin{itemize}
%   \item{\url{https://github.com/alibaba/code-data-share-for-python}}
% \end{itemize}

\datedsubsection{\textbf{Oracle Labs}, Zurich, Switzerland}{09/2020 -- 02/2021}
\role{Student Intern}{Loom support for Graal Native Image (AOT compilation of coroutine in Java)}
\begin{itemize}
	\item{\url{https://github.com/oracle/graal/commits?author=oraluben}}
\end{itemize}

\datedsubsection{\textbf{PingCAP}, remote}{06/2020 -- 08/2020, 05/2021 -- 07/2021}
\role{Intern}{Improve stability of TiDB with fuzzing-based approaches.}
\begin{itemize}
	\item{Design and implement a configuration-oriented fuzzing tool Matrix. (2020)}
	\item{Introduce state-of-the-art fuzzing approaches to test SQL layer of TiDB. (2021)}
\end{itemize}

\datedsubsection{\textbf{ETH Zurich} Zurich, Switzerland}{05/2019 -- 12/2019}
\role{Visiting Student}{Research in programming language and testing in Prof. Zhendong Su's group.}
\begin{itemize}
	\item{TA of Compiler Design, fall 2019.}
\end{itemize}

% \datedsubsection{\textbf{Splunk} Shanghai, China}{07/2017 -- 01/2018}
% \role{Intern}{Working in performance group.}
% \begin{itemize}
%   \item{Responsible for a part of feature and test case developing.}
%   \item{Introduce coverage-based unit/integration test, which helped to find serious bugs.}
% \end{itemize}

%\datedsubsection{\textbf{Intel} Shanghai, China}{06/2015 -- 09/2016}
%\role{Intern}{Working on iLab, a web-based private cloud platform globally used in Intel.}
%\begin{itemize}
%  \item{Responsible for a part of feature developing and bug fix for web and SDK.}
%  \item{Developed a POC of server communication protocol based on ActiveMQ.}
%\end{itemize}

\section{Education}
\datedsubsection{\textbf{East China Normal University}, Shanghai, China}{09/2017 -- 03/2022}
\textit{M.S.} in Software Engineering (SE)
\datedsubsection{\textbf{East China Normal University}, Shanghai, China}{09/2013 -- 06/2017}
\textit{B.S.} in Software Engineering (SE)

\section{Projects}
% \datedsubsection{\textbf{Matrix}}{\url{https://github.com/chaos-mesh/matrix}}
% \role{Golang}{Matrix is a fuzz-testing tool targeting configurations that generate config files based on a DSL.}
% \begin{itemize}
% 	\item{Design DSL based on requirement;}
% 	\item{Implement with Golang}
% \end{itemize}

\datedsubsection{\textbf{MC Fuzz}}{\url{https://tingsu.github.io/files/fse19-MCFuzz.pdf}}
\role{Python / C++ / Clang / Docker}{Design and implement MCFuzz to fuzz and test Model Checkers. The tool takes a general C source code to generate test cases for model checker.}
\begin{itemize}
  \item{Well designed and easy to extend to other fuzzing strategy/model checkers.}
  \item{Docker based isolation.}
\end{itemize}

\datedsubsection{\textbf{Voile}}{\url{https://github.com/owo-lang/voile-rs}}
\role{Rust}{Voile is a dependently-typed programming language features in first-class sums and records.}
\begin{itemize}
  \item{Dependent type-checking;}
  \item{Implicit argument checking.}
\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.25ex]
  \item \textbf{Programming Languages}:
    Experienced in Python, confortable with C++/C\#/Java/Rust/OCaml/Go.

  \item \textbf{Compilers}:
    Solid knowledge of compiler, familiar with GraalVM and Clang/LLVM toolchain.
  
  \item \textbf{Developing Experience}:
    Have experience with various type of projects, including but not limited to web (Angular/Vue/PHP/Python), client-side program for different perpous and online game (WebSocket, HTML5).

  \item \textbf{Developing Tools}:
    Familiar with git workflow and have experience with team tools like YouTrack, Jira, GitHub.
    % Also experienced with IDEs, e.g. Jetbrains, Visual Studio (Code) and Eclipse.
  
  \item \textbf{Programming Style}:
    Experienced in writing well-documented or easy-understanded code.
  
  \item \textbf{Language and Communication}:
    Fluent in English, and willing to cooperate with others in team.
  
  \item \textbf{Problem Solving}:
    Able to identify and solve problems in computer science and programming fields.
\end{itemize}

\section{Miscellaneous}
\begin{itemize}[parsep=0.25ex]
  \item Opensource Contribution: contributed to Graal, LLVM/Clang, Python and some other projects.
\end{itemize}

\section{Publications}
\input{pubs.tex}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}

